\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-02-01 manuscript.Rmd
correlation range amended
Correlation Matrix with Histogram

min.cor <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
max.cor <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix

@@

>>>>

min.cor <- apa(min((upper)),2,F) #minimum cor.coefficient of the matrix
max.cor <- apa(max((upper)),2,F) # max. correlation coefficient of the matrix

@@

```{r correlation-hits, include=F}
#This chunk holds code for plotting the correlation matrix in histogram format

cor.hits <- as.data.frame(melt(upper))
colnames(cor.hits) <- c("value")
corr.histogram <- ggplot(cor.hits,aes(x=value)) + 
  geom_histogram(binwidth=.1, col=I("black"),fill="#00A08799")+apatheme+
  labs( y="", x = "Inter-item correlation")

ggsave("Manuscript.figures/correlation_histogram.png", corr.histogram, width = 6, height = 6, dpi = 600, bg ="white")
```
